Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-14 VMCAI-revised-version/final.tex
section

With the ideal-effective hypothesis, we obtain the decidability of coverability for a class of ordered transition systems larger than WSTS.

\begin{theorem}\cite{BFM-ic17}
Coverability is decidable for any ideal-effective ordered upward-compatible transition system $\mathscr{S}=(S, \rightarrow, \leq)$ where $\leq$ is without infinite antichains.
\end{theorem}

>>>>

Let us recall that a Well Behaved Transition Systems (WBTS) \cite{DBLP:journals/lmcs/BlondinFM17} is an upward compatible ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ where $(S,\leq)$ contains no infinite antichains (but it can be not well founded). The class of WBTS is strictly larger than WSTS: for example, integer VASS under the lexicographical ordering are WBTS but not WSTS \cite{DBLP:journals/lmcs/BlondinFM17}. 
With the ideal-effective hypothesis, we obtain the decidability of coverability for WBTS.

\begin{theorem}\cite{DBLP:journals/lmcs/BlondinFM17}
Coverability is decidable for any ideal-effective WBTS.
\end{theorem}
